Proof by reflection for equalities in algebraic structures

### 2014-06-16 newPaper/paper.tex
file Autoassoc with change for constant list

>>>>

We will start with the study of a smaller problem in which we aim to deal with lists, and associativity of list concatenation.
For example, we would like to be able to generate automatically proofs of facts like $\forall l1\ l2\ l3 : List,\ (l1 ++ l2) ++ (l3 ++ l4) = (l1 ++ (l2 ++ l3)) + l4$. \\
For this smaller problem, we have decided to only work with the associativity of concatenation : $\forall l1\ l2\ l3,\ (l1 ++ l2) ++ l3 = l1 ++ (l2 ++ l3)$.
So, in definitive, in this section, we want to write a decision procedure, able to say if to two expressions composed of lists and concatenation of lists are equal, when "equal" has the meaning "syntactically equal or equal thanks to associativity".

The general idea -which will also apply for the real problem- will be to normalize both sides of the "potential equality" $l1=l2$, and afterwards to compare them using Leibniz syntactical equality.
Of course, the normalization will have to fulfil the following property :
$\forall l, norm\ l = l$ [1], which means that after normalization we obtain a list which is provably equal to the input's list. \\
After normalization, we will compare the two resulting lists, and if they are equal, we will have obtained the corresponding proof.  \\
Indeed :
$norm\ l1 = norm\ l2$ will imply $l1=l2$ by [1].

In fact, this is not really how it will be, because as for the real problem, we will work by reflection. The datatype presented in the Listing 1 is a first approximation what we will use to reflect out terms composed of lists and concatenation of lists.

\begin{lstlisting}[caption=Reflected lists, captionpos=b, label=lst1:haskell2]
data Expr : Type where
	App  : Expr -> Expr -> Expr 
	Var  : (i : Fin n) -> Expr
    ENil : Expr
\end{lstlisting}
